%-------------------------
% Cover Letter in Latex
% Author : Ali Abdullah Khan
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{fontspec}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright

\begin{document}

\begin{center}
    \textbf{\Large Ali Abdullah Khan} \\[4pt]
    \small
    929-444-2248 \textbar{}
    \href{mailto:abdullah017196@gmail.com}{abdullah017196@gmail.com} \textbar{}
    \href{https://www.linkedin.com/in/abdullah017196}{linkedin.com/in/abdullah017196} \textbar{}
    \href{https://alikhan.dev}{alikhan.dev} \\[2pt]
    Holbrook, New York, USA \textbar{} U.S. Citizen -- No sponsorship required
\end{center}

\vspace{20pt}

\today

\vspace{20pt}

Dear Hiring Manager,

\vspace{10pt}

I am writing to express my interest in the Software Engineering role at your organization. With over seven years of experience delivering high-scale consumer banking and payment products at JPMorgan Chase \& Co. --- including platforms serving approximately one million daily users --- I bring a strong track record of leading full product lifecycles from planning and architecture through delivery and production support.

\vspace{8pt}

In my current role as Vice President, Software Engineering, I lead the development of Payment Activity and Transfer Activity experiences across the consumer banking platform. I drive an agentic, AI-assisted software development lifecycle using GitHub Copilot and a structured knowledge base, automating requirements intake, PRD generation, task decomposition, and code delivery, alongside AI-assisted test generation across unit, component, and end-to-end suites. This approach has significantly reduced cycle time from requirements to production and improved regression confidence across my team.

\vspace{8pt}

Beyond feature delivery, I have built internal CLI tooling for production CDN artifact publishing and feature flag management, enabling self-service deployments and eliminating manual release steps. I also own end-to-end execution across roadmap planning, sprint delivery, and cross-functional stakeholder alignment, while establishing front-end engineering standards and mentoring associate engineers to strengthen code quality, accessibility, and delivery consistency.

\vspace{8pt}

My technical expertise spans JavaScript, TypeScript, React, Node.js, and AWS, with a deep commitment to accessibility-first engineering and WCAG compliance. I hold an AWS Certified Cloud Practitioner certification and a Bachelor of Science in Computer Science and Engineering.

\vspace{8pt}

I am excited about the opportunity to bring my experience in building scalable platforms, leading engineering teams, and leveraging AI-augmented workflows to your organization. I would welcome the chance to discuss how my background aligns with your team's goals.

\vspace{16pt}

Sincerely,

\vspace{4pt}

Ali Abdullah Khan

\end{document}
